The case for open preprints in biology

### 2013-03-20 ms.tex
figshare now supports private documents

\begin{table}[!ht]
  \caption{\bf{Popular options for preprints}}
  \begin{tabular}{|l|ccccccc|}
  \hline
  Website               & Free & Comments & Private & P.-R. & DOI & V.C. & O.C.\\
  \hline
  arXiv.org             & Yes & No & No & No & No & No & No\\
  figshare.com          & Yes & Yes & No & No & Yes & No & Yes\\
  peerj.com             & 1/yr & Yes & Yes & No & Yes & No & No\\
  f1000research.com     & No & Yes & No & Yes & Yes & No & No\\
  github.com            & Yes & Yes & Yes & No & No & Yes & Yes\\
  \hline
  \end{tabular}
  \caption{
    \textbf{Free:} Can preprints be submitted for free.
    \textbf{Comments:} Support for online comments.
    \textbf{Private:} Support for private preprints.
    \textbf{P.-R.:} Whether the preprints are peer-reviewed on the server.
    \textbf{DOI:} Each item is assigned a unique digital object identifier.
    \textbf{V.C.:} Is the preprint stored using a version-control system with the complete history of modifications?
    \textbf{O.C.:} Can upload figures, videos, datasets, code.
  }
  \label{table:options}
\end{table}

>>>>

\begin{table}[!ht]
  \caption{\bf{Popular options for preprints}}
  \begin{tabular}{|l|ccccccc|}
  \hline
  Website               & Free & Comments & Private & P.-R. & DOI & V.C.& O.C.\\
  \hline
  arXiv.org             & Yes  & No       & No      & No    & No  & No  & No\\
  figshare.com          & Yes  & Yes      & Yes     & No    & Yes & No  & Yes\\
  peerj.com             & 1/yr & Yes      & Yes     & No    & Yes & No  & No\\
  f1000research.com     & No   & Yes      & No      & Yes   & Yes & No  & No\\
  github.com            & Yes  & Yes      & Yes     & No    & No  & Yes & Yes\\
  \hline
  \end{tabular}
  \caption{
    \textbf{Free:} Can preprints be submitted for free.
    \textbf{Comments:} Support for online comments.
    \textbf{Private:} Support for private preprints.
    \textbf{P.-R.:} Whether the preprints are peer-reviewed on the server.
    \textbf{DOI:} Each item is assigned a unique digital object identifier.
    \textbf{V.C.:} Is the preprint stored using a version-control system with the complete history of modifications?
    \textbf{O.C.:} Can upload figures, videos, datasets, code.
  }
  \label{table:options}
\end{table}
